### 2022-04-27 sections/summary.tex
Update summary.tex
LPPL v1.3c

%% Creative Commons Attribution 4.0 International License
%% https://github.com/bgonzalezbustamante/CV-XeLaTeX/blob/master/LICENSE.txt

@@

I am completing my DPhil (PhD) dissertation in the Department of Politics and International Relations and St Hilda’s College at the University of Oxford, United Kingdom. I am currently based in Oxford, working on my research. Furthermore, I am an Instructor Professor in the Management and Public Policies Department at the Faculty of Administration and Economics at the Universidad de Santiago de Chile.

@@

My doctoral research is supervised by Professor Petra Schleiter and focuses on cabinets’ stability in Latin American presidential democracies. In my DPhil project, I combine the principal-agent theory elements to evaluate the actors’ incentives and strategies in presidential systems. My empirical strategy employs propensity scores and matching methods, competing risks models, and IV estimations. My research is funded by the Chilean National Agency for Research and Development.
\vspace{1mm}
\end{cvparagraph}

>>>>

%% LaTeX Project Public License v1.3c
%% https://github.com/bgonzalezbustamante/CV-XeLaTeX/blob/master/LICENSE.md

@@

I am completing my DPhil (PhD) dissertation in the Department of Politics and International Relations and St Hilda’s College at the University of Oxford, United Kingdom. I am currently based in Oxford, working on my research. Furthermore, I am an Instructor Professor in the Management and Public Policies Department at the Faculty of Administration and Economics at the Universidad de Santiago de Chile (USACH).

@@

My doctoral research is supervised by Professor Petra Schleiter and focuses on cabinets’ stability in Latin American presidential democracies. In my DPhil project, I combine the principal-agent theory elements to evaluate the actors’ incentives and strategies in presidential systems. My data gathering strategy is based on archives revision using Optical Character Recognition (OCR), Natural Language Processing (NLP), and machine learning techniques. In addition, my empirical strategy employs propensity scores and matching methods, competing risks models, and IV estimations.

My research is funded by the Chilean National Agency for Research and Development and the St Hilda’s College Muriel Wise Fund.
\vspace{1mm}
\end{cvparagraph}
